Preregistration: data extraction from epidemiology articles

### 2020-01-22 qualtrics_forms/prereg_data_extraction.Rmd
final prereg version and rename qualtrics forms

---
title: "Preregistration: data extraction from epidemiology articles"
author: "Katie Drax"
date: "9 January 2020"
output: word_document
---

@@

The information in Table 1 (attached) will be extracted manually by KD or automatically by Endnote which contains the article's metadata exported from the database the article was located in.

@@

| Item | Definition | Method of extraction |
| --- | --- | --- |
| Article ID(s) of related articles | Article IDs of articles that contain similar analyses. | Examine articles with same first author, last author and UK Biobank application number. |
| Citation |   | Endnote |
| Publication date |   | Endnote |
| Authors |   |  Endnote |
| Journal |   | Endnote  |
| Volume |   | Endnote  |
| Issue |   | Endnote  |
| Open Access |   | See if can access article on publishing journal's site on a non-university network. If not accessible search for self-archived version on Google Scholar |
| Countries of corresponding author |   | Extract country from author's affiliations |
| UK Biobank Application number | Study's approved UK Biobank data application number (if present) | Search article for all these terms:  'application' , 'approv' , 'number' , 'Resource'. If not found examine any strings of numbers in article |
| Author keywords |   | Search page 1. If not on page 1 search article for 'keywords' |
| Journal endorsement | Journal's endorsement of STROBE before publication | Extract references to STROBE from the journal's most recent 'instructions/guide for authors' before article's publication date |
| Journal impact factor |   | Retrieve the impact factor of the journal for year of publication from Web of Science's Journal Citation Reports (JCR) |
| Corresponding author email address |   | Search article for 'corresponding', '@') |
| Conflicts of interest statement |   | Search article material for all these terms: 'competing', 'interest' ,'conflict' , 'disclosure' |
| Classification | Classification ('mendelian randomisation', 'observational epidemiology' or 'other') as assigned by KD, BW and RR in Rayyan | Rayyan

>>>>

---
title: "Preregistration: data extraction from epidemiology articles"
author: "Katie Drax"
date: "9 January 2020"
output: pdf_document
---

@@

The items in Table 1 will be extracted manually by KD or automatically by Endnote which contains the article's metadata exported from the database the article was located in.

@@

| Item | Definition | Method of extraction |
| --- | --- | --- |
| Article ID(s) of related articles | Article IDs of articles that contain similar analyses. | Examine articles with same first author, last author and UK Biobank application number. |
| Citation |   | Endnote |
| Publication date |   | Endnote |
| Authors |   |  Endnote |
| Journal |   | Endnote  |
| Volume |   | Endnote  |
| Issue |   | Endnote  |
| Open Access |   | See if can access article on publishing journal's site on a non-university network. If not accessible search for self-archived version on Google Scholar |
| Country | Countries of corresponding author | Extract country from corresponding author's affiliations |
| UK Biobank Application number | Study's approved UK Biobank data application number (if present) | Search article for all these terms:  'application' , 'approv' , 'number' , 'Resource'. If not found examine any strings of numbers in article |
| Author keywords |   | Search page 1. If not on page 1 search article for 'keywords' |
| Journal endorsement | Journal's endorsement of STROBE before publication | Extract references to STROBE from the journal's most recent 'instructions/guide for authors' before article's publication date |
| Journal impact factor |   | Retrieve the impact factor of the journal for year of publication from Web of Science's Journal Citation Reports |
| Corresponding author email address |   | Search article for 'corresponding', '@' |
| Conflicts of interest statement |   | Search article material for all these terms: 'competing', 'interest' ,'conflict' , 'disclosure' |
| Classification | Classification assigned by KD, BW and RR in Rayyan | Rayyan
